\documentclass[10pt,twoside,english,a4paper]{article}

\usepackage[english]{babel}
\usepackage[IL2]{fontenc}
\usepackage[utf8]{inputenc}
\usepackage{graphicx}
\usepackage{url}
\usepackage{hyperref}
\usepackage{cite}
\usepackage{times}
\usepackage{indentfirst}

\pagestyle{headings}

\title{The influence of video games on people and the human psyche\thanks{Semester project in the subject Methods of engineering work, ac. year 2022/23, management: Ing. Igor Stupavsky}}

\author{Erik Roganský\\[2pt]
	{\small Slovak University of Technology in Bratislava}\\
	{\small Faculty of Informatics and Information Technologies}\\
	{\small \texttt{xrogansky@stuba.sk}}
	}

\date{\small October 11, 2022}


\begin{document}

\maketitle

\begin{abstract}
\ldots
\end{abstract}



\section{Introduction}
Over the last few, video games have started to gain popularity, and the increase is far from stopping. In the past, not many people could afford to play video games. Computers were exceedingly expensive, and gaming consoles were no better. As time passed, electronic devices became more affordable for everyone. The age range of video game players is also expanding precipitously. Video games, in general, were designed to entertain teenagers and young adults. These days, it is not uncommon to find a toddler playing with a smartphone, a mature adult sitting in front of television playing games on a console, or even an elder, playing on a computer. As video games are expanding among more and more people, their influence, whether it is positive or negative, is also getting more vast. That is why we should focus more on the issue of video games and their impacts on humans, which will be the main topic of this work.

\section{The influence of games on the child development} %\label{part1}
\ldots

\section{The influence of games on the adults' behavior}
\ldots

\section{Changes in empathy due to video games}
\ldots

\section{Positive effect on humans}
Growing popularity makes video games an excellent tool that can be used in various positive ways. They have the power to improve the quality of life in an abundance of aspects. Some studies, for example, researched how violent games affect people, and the outcome is remarkable. They found out that games containing violence do not lead to aggression but, on the contrary, improve visuospatial skills. Another study discovered that seniors who regularly or at least occasionally play video games witness better well-being and experience less depression than those who do not.~\cite{poz-neg-sol}


\subsection{Socializing via video games}
As far as society remembers, games played a vital role in socializing. The first game is dated back to ancient times. People played games to meet others and to entertain each other. People created many meaningful bonds through playing games. As time has passed and we have come to a digital era, video games have started to dominate over classical games. In the matter of socializing, MMO (Massively Multiplayer Online) games are one of the best ways to meet people online. They are designed to be social on a massive scale. MMO games are technically a space with hundreds of people that play together, competitively or cooperatively. While meeting people via video games may not be the same as shared experiences, friendships established through playing video games can be similarly meaningful. Additionally, people having difficulties establishing normal relationships can also benefit from playing these games because they make it for them to talk through the game than face to face.~\cite{poz-neg-sol}

\subsection{Education}
\ldots


\subsection{Foreign language learning}
\ldots


\section{Negative effects on humans}
\ldots

\subsection{Addiction}
\ldots

\subsection{Obesity}
\ldots

\section{Conclusion} \label{conclusion}
\ldots

\section*{Citations} \label{cit} 
~\cite{school,behavior,education,empathy,problems,poz-neg-sol,language,learning}


\bibliography{literatura}
\bibliographystyle{acm}
\end{document}
